---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# tcplspclient

<!-- badges: start -->
<!-- badges: end -->

A TCP client for corresponding with R's language server enabling interactive debugging.

## Installation

```{r eval = FALSE}
pak::pkg_install("milesmcbain/tcplspclient")
```

## Usage

In R session 1 (client):

1. Start the client. (It's technically the server. Good one Microsoft.)

```{r eval = FALSE}
library(tcplspclient)
client <- TCPLanguageClient$new(host = "localhost", port = 8888)

```

In R session 2 (server):

0. `devtools::load_all()`
0. Add `browser()` statements or use `debugonce()`/`debug()` etc to `languageserver` functions.
1. Connect the language server to the client:

```{r eval = FALSE}
run(port = 8888)
```

In R session 1  (client)


1. Do handshake.

```{r eval = FALSE}
# TCP client connected to localhost:8888
server_capabilities <- client$handshake()

server_capabilities
# $textDocumentSync
# $textDocumentSync$openClose
# [1] TRUE

# $textDocumentSync$change
# [1] 1

# $textDocumentSync$willSave
# [1] FALSE

# ...
```

2. Send messages to trigger server actions to debug in session 2.
  - note see [this file](https://github.com/REditorSupport/languageserver/blob/master/tests/testthat/helper-utils.R) for protocol wrapper functions.

```{r eval = FALSE}
doc_path <- "~/code/r/blogdown_test/content/post/test2.R"

client$send_notification(
        method = "textDocument/didSave",
        params  = list(textDocument = list(
          uri = languageserver:::path_to_uri(doc_path)), 
          text = paste0(stringi::stri_read_lines(doc_path), collapse = "\n")
        )
)

response <- client$send_message(
        method = "textDocument/documentSymbol",
        params = list(
            textDocument = list(uri = 
                languageserver:::path_to_uri("~/code/r/blogdown_test/content/post/test2.R"))
        )
    )
```

Now debug interactively in R session 1. Eventually get the response you expected:

```{r eval = FALSE}
response

# response
# [[1]]
# [[1]]$name
# [1] "f"

# [[1]]$kind
# [1] 12

# [[1]]$location
# [[1]]$location$uri
# [1] "file:///home/miles/code/r/blogdown_test/content/post/test2.R"

# [[1]]$location$range
# [[1]]$location$range$start
# [[1]]$location$range$start$line
# [1] 0

# [[1]]$location$range$start$character
# [1] 0
```


## Licenses

Code in this project is substantially copied from the [{languageserver}](https://github.com/REditorSupport/languageserver). Code files carry approriate licenses and attribution in header comments.
